---
title: "ASSIST - results"
output: pdf_document
---
```{r}
library(knitr)
library(kableExtra)
```

```{r, include=FALSE}
rm(list = ls())
source("/Volumes/dcn_assist-8/PROCESSING/scripts/PROCESSING_MAIN_ASSIST.R", echo = F, print.eval = F)
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Descriptives 
Descriptive statistics
```{r, echo = F}
kable(datAnalyse_mean, col.names =(rep("",ncol(datAnalyse_mean))),
      caption="Means", row.names=T)%>% 
column_spec(1,width = "2in")%>%
column_spec(2:6,width = "0.5in")
```

```{r, echo = F}
kable(datAnalyse_sd, col.names =(rep("",ncol(datAnalyse_sd))),
      caption="SDs", row.names=T)%>% 
column_spec(1,width = "2in")%>%
column_spec(2:6,width = "0.5in")
```

\clearpage

## Plots

Plot of outcomes
\newpage
```{r, echo=F}
grid.draw(bf2)
```
\newpage
```{r, echo=F, fig.height = 15, fig.width = 15}
grid.draw(bf3)
```
\newpage
```{r, echo=F}
grid.draw(bf4)
```

\newpage
## Regression
Output of regression model, which was:
lme(DV ~  Age + factor(Sex) + factor(Condition) * factor(Intervention_Phase))
if interaction is not significant, the model is recalculated without the interaction term


```{r, echo = F}
first_third <- c(1:(nrow(res_all_DV)/3))
second_third <- c(nrow(res_all_DV)/3+1):(nrow(res_all_DV)/3*2)
last_third <- c(nrow(res_all_DV)/3*2+1):(nrow(res_all_DV))
kable(cbind(res_all_DV[first_third, c("DV","IVs")], round (res_all_DV[first_third,c("Pr(>Chisq)", "t-value", "r")], digits = 4)), caption="Regression Results", row.names=F)%>%
kable_styling(font_size = 7,   latex_options = "scale_down")
```
```{r, echo = F}
kable(cbind(res_all_DV[second_third, c("DV","IVs")], round (res_all_DV[second_third,c("Pr(>Chisq)", "t-value", "r")], digits = 4)), caption="Regression Results", row.names=F)%>%
kable_styling(font_size = 7,   latex_options = "scale_down")
```
```{r, echo = F}
kable(cbind(res_all_DV[last_third, c("DV","IVs")], round (res_all_DV[last_third,c("Pr(>Chisq)", "t-value", "r")], digits = 4)), caption="Regression Results", row.names=F)%>%
kable_styling(font_size = 7,   latex_options = "scale_down")
```


res_sub_all_DV
main_effects_all
sub_effects_all
summary_N_all